Combine_results

### 2017-03-28 Code/examining_heterogeneity.Rmd
heterogeneity analysis

cod_decomp_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_decomp_results.csv")
```

```{r modeling}
#run 12 stratified models. bs() created the b-spline basis
models <- cod_decomp_results %>% 
  group_by(COD, sex) %>%
  do(fit = lm(COD_cont_yrs_mean ~ bs(year, degree = 1, df = 5) + state, data = .))

@@

  a <- ggplot(subset.data,
         aes(x = year, y = COD_cont_yrs_mean)) + geom_line(aes(col = "Observed")) + 
    facet_wrap( ~ order) + 
    geom_line(aes(y = .fitted, col = "Estimated")) +
    xlab(" ") + ylab("observed vs. estimated contribution (years)") + 
    ggtitle(paste0("Observed vs. estimated in ", COD1, " in ", sex1)) +
    theme_minimal() + theme(axis.text.x = element_text(angle = 45, hjust = 1))

  b <- ggplot(subset.data,
              aes(x = year, y = .resid)) + geom_line(aes(col = "Residual")) + 
    facet_wrap( ~ order) +
    xlab(" ") + ylab("Residual") +
    geom_hline(yintercept = 0, col = "black") +
      geom_text(data = subset(subset.data, year == 2010), 
                aes(y = 1, label = round(sum.residual, 1)), size = 2.5) + 
    ggtitle(paste0("Residuals vs. year in ", COD1, " in ", sex1)) +
    theme_minimal() + theme(axis.text.x = element_text(angle = 45, hjust = 1))

>>>>

cod_decomp_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_decomp_results.csv")

cod_decomp_results$COD_cont_yrs_width <- cod_decomp_results$COD_cont_yrs_ucl - cod_decomp_results$COD_cont_yrs_lcl
cod_decomp_results$COD_cont_yrs_SE1 <- (cod_decomp_results$COD_cont_yrs_ucl - cod_decomp_results$COD_cont_yrs_mean)/1.96
cod_decomp_results$COD_cont_yrs_SE2 <- -(cod_decomp_results$COD_cont_yrs_lcl - cod_decomp_results$COD_cont_yrs_mean)/1.96
cod_decomp_results$SE.diff <- cod_decomp_results$COD_cont_yrs_SE1 - cod_decomp_results$COD_cont_yrs_SE2
summary(cod_decomp_results$SE.diff)

# cod_decomp_results.means <- cod_decomp_results %>% 
#   mutate(COD_cont_yrs_width = COD_cont_yrs_ucl - COD_cont_yrs_lcl) %>%
#   group_by(state, sex, COD) %>%
#   summarise(mean_COD_cont_yrs_width = mean(COD_cont_yrs_width))
# 
# mod1 <- lm(COD_cont_yrs_mean ~ bs(year, degree = 1, df = 5) + state, data = subset.data)
# 
# mod2 <- lm(COD_cont_yrs_mean ~ bs(year, degree = 1, df = 5) + state, weights = 1/(COD_cont_yrs_SE1)^2, 
#            data = subset.data)
```

```{r modeling}
#run 12 stratified models. bs() created the b-spline basis
models <- cod_decomp_results %>% 
  group_by(COD, sex) %>%
  do(fit = lm(COD_cont_yrs_mean ~ bs(year, degree = 1, df = 5) + state, 
              weights = 1/(COD_cont_yrs_SE1)^2, 
              data = .))

@@

  a <- ggplot(subset.data,
         aes(x = year, y = COD_cont_yrs_mean)) + 
    #geom_line(aes(col = "Observed")) + 
    geom_ribbon(aes(ymin = COD_cont_yrs_lcl, ymax = COD_cont_yrs_ucl), fill = "#b2e2e2") +
    #scale_fill_manual(values = c("#b2e2e2")) +
    facet_wrap( ~ order) + 
    geom_line(aes(y = .fitted), col = "#006d2c") +
    #scale_color_manual(values = c("#006d2c")) +
    xlab(" ") + ylab("observed vs. estimated contribution (years)") + 
    ggtitle(paste0("Observed vs. estimated in ", COD1, " in ", sex1)) +
    theme_minimal() + theme(axis.text.x = element_text(angle = 45, hjust = 1))

  b <- ggplot(subset.data,
              aes(x = year, y = .resid)) + geom_line(aes(col = "Residual")) + 
    scale_color_manual(values = c("#006d2c")) +    
    facet_wrap( ~ order) +
    xlab(" ") + ylab("Residual") +
    geom_hline(yintercept = 0, col = "black") +
      geom_text(data = subset(subset.data, year == 2010), 
                aes(y = 1, label = round(sum.residual, 1)), size = 2.5) + 
    ggtitle(paste0("Residuals vs. year in ", COD1, " in ", sex1)) +
    theme_minimal() + theme(axis.text.x = element_text(angle = 45, hjust = 1))
